### 2013-11-28 manuscripts/reply/reply.tex
Working on reply ms.
Working on section about theory of empirical Bayesian model choice.
author line fix

        \vspace{12pt}
        Jamie R.\ Oaks$^{1,2}$, Jeet Sukumaran$^{3}$, Jacob A.\
        Esselstyn$^{4}$, Charles W.\ Linkem$^{5}$, Cameron D.\
        Siler$^{6}$, Rafe M.\ Brown$^{1}$ and Mark T.\ Holder$^{1}$

@@

>>>>

        \vspace{12pt}
        Jamie R.\ Oaks$^{1,2}$, Jeet Sukumaran$^{3}$, Jacob A.\
        Esselstyn$^{4}$, Charles W.\ Linkem$^{5}$, Cameron D.\
        Siler$^{6}$, and Rafe M.\ Brown$^{1}$

@@

\newpage
\singlespacing

\input{reply-si-figures.tex}
